---
title: "Differential abundance analysis"
author: "Kaushik Amancherla"
date: "2024-03-19"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(Seurat)
library(miloDE)
library(miloR)
library(SingleCellExperiment)
library(S4Vectors)
library(BiocParallel)
library(ggpubr)
library(gprofiler2)

# Set working directory
setwd("C:/Users/amanchk/Downloads/PBMC_CAV_2.2024")
```

## Load PBMC CAV Seurat object and convert to SCE

Here, I am just loading the object that I previously created. Once loaded, I will convert it to a SingleCellExperiment (SCE) object that can be used for downstream analyses.

```{r}
# Load Seurat object
pbmc <- readRDS("Processing_RDS_files/2024_pbmc_ALL_samples_postANNOTATION.rds")

# Rename two metadata columns for easier downstream analyses
pbmc@meta.data <- pbmc@meta.data %>% dplyr::rename(
  cluster = predicted.celltype.l1,
  subcluster = predicted.celltype.l2
)

# Convert the Seurat object to an SCE object
pbmc.sce <- as.SingleCellExperiment(pbmc, assay = "RNA")
pbmc.sce

# Convert to Milo object
pbmc.milo <- Milo(pbmc.sce)
pbmc.milo
```

## Constructing the KNN graph

You can also embed plots, for example:

```{r}
set.seed(42) # Set seed for reproducibility

# Build the graph
pbmc.milo.k90 <- buildGraph(pbmc.milo, k = 90, d = 30)
```

Next, we will define representative neighborhoods:
```{r}
pbmc.milo.k90 <- makeNhoods(pbmc.milo.k90, k = 90, d = 30, prop = 0.1, refined = TRUE, reduced_dims = "HARMONY")

# Plot
plotNhoodSizeHist(pbmc.milo.k90) +
  scale_x_continuous(limits=c(0, 500))
```

The majority of neighborhoods have size peaking between 50 and 100, as recommended by miloR.

Now, we count the number of cells in the neighborhoods:
```{r}
pbmc.milo.k90 <- countCells(pbmc.milo.k90, meta.data = data.frame(colData(pbmc.milo.k90)), samples="Sample_ID")

# Look at count matrix for DA analysis
head(nhoodCounts(pbmc.milo.k90))
```

## Differential abundance testing

First, we create the design for the DA testing. I will use "group" (CAV vs Control) as the covariate.

```{r}
design <- data.frame(colData(pbmc.milo.k90))[,c("Sample_ID", "high_grade_cav")]
design <- distinct(design)
rownames(design) <- design$Sample_ID

# Factor
design$high_grade_cav <- factor(design$high_grade_cav, levels = c("0", "1"))
levels(design$high_grade_cav)

## Reorder rownames to match columns of nhoodCounts(milo)
design <- design[colnames(nhoodCounts(pbmc.milo.k90)), , drop=FALSE]

design
```

Now, we run DA analysis using condition as the covariate:
```{r}
gc()
pbmc.milo.k90 <- calcNhoodDistance(pbmc.milo.k90, d=30, reduced.dim = "HARMONY")
pbmc.milo.k90

# saveRDS(pbmc.milo.k90, "Processing_RDS_files/miloR/pbmc.miloR.d30.k90.rds")
```

Perform the DA analysis:
```{r}
da_results <- testNhoods(pbmc.milo.k90, design = ~ high_grade_cav, design.df = design)

# Look at the DA results
da_results %>%
  arrange(- SpatialFDR) %>%
  head()

# Save DA results
# write_csv(da_results, "Processing_RDS_files/miloR/High_grade_DA_results_6.2.24_k90.csv")
```
## Visualization of DA results

First, inspect the DA results:
```{r}
ggplot(da_results, aes(PValue)) + geom_histogram(bins=50)

# Volcano plot (each point represents a neighborhood, not cell)
ggplot(da_results, aes(logFC, -log10(SpatialFDR))) + 
  geom_point() +
  geom_hline(yintercept = -log10(0.1)) ## Mark significance threshold (10% FDR)
```

Next, visualize the DA results:
```{r}
pbmc.milo.k90 <- buildNhoodGraph(pbmc.milo.k90)

## Plot single-cell UMAP
umap_pl <- scater::plotReducedDim(pbmc.milo, dimred = "UMAP", colour_by="subcluster", text_by = "subcluster", 
                          text_size = 3, point_size=0.5) +
  guides(fill="none")

## Plot neighbourhood graph
nh_graph_pl <- plotNhoodGraphDA(pbmc.milo, da_results, layout="UMAP",alpha=0.05) 
  
umap_pl + nh_graph_pl +
  patchwork::plot_layout(guides="collect")
```

Next, I will plot the DA results according to cell type in an easily-digestible manner:
```{r}
# Add cell type annotation
da_results <- annotateNhoods(pbmc.milo.k90, da_results, coldata_col = "subcluster")
head(da_results)

# Inspect subcluster fraction
ggplot(da_results, aes(subcluster_fraction)) + geom_histogram(bins=50)
# ggsave("Figures/MiloR_subcluster_fraction_distribution_k90.png", dpi = 1200, bg = "white")

# Change class of subcluster column to factor
da_results$subcluster <- as.factor(da_results$subcluster)

# Visualize
miloR::plotDAbeeswarm(da_results, group.by = "subcluster")
# ggsave("Figures/MiloR_high_grade_k90.png", dpi = 1200, bg = "white")

# Use 0.7 as the cut-off
da_results_cutoff <- da_results
da_results_cutoff$subcluster <- ifelse(da_results_cutoff$subcluster_fraction < 0.7, "Mixed", da_results_cutoff$subcluster)


# Visualize
miloR::plotDAbeeswarm(da_results_cutoff, group.by = "subcluster")
# ggsave("Figures/MiloR_high_grade_k90_mixed.png", dpi = 1200, bg = "white")
```

Further investigation of DA neighborhoods - why do some have both increased and decreased DA in high-grade CAV? This includes CD4 TCM, CD14 and CD16 monocytes
```{r}

```

Save rds file:
```{r}
gc()
# saveRDS(pbmc.milo, "Processing_RDS_files/miloR/pbmc.milo_high_grade_d30_6.1.24.RDS")
```