---
title: "PBMC CAV Different gene expression"
author: "Kaushik Amancherla"
date: "2024-03-09"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(Seurat)
library(miloDE)
library(miloR)
library(SingleCellExperiment)
library(S4Vectors)
library(BiocParallel)
library(ggpubr)
library(gprofiler2)

# Set working directory
setwd("C:/Users/amanchk/Downloads/PBMC_CAV_2.2024")
```

## Load PBMC CAV Seurat object and convert to SCE

Here, I am just loading the object that I previously created. Once loaded, I will convert it to a SingleCellExperiment (SCE) object that can be used for downstream analyses.

```{r}
# Load Seurat object
pbmc <- readRDS("Processing_RDS_files/2024_pbmc_ALL_samples_postANNOTATION.rds")

# Rename two metadata columns for easier downstream analyses
pbmc@meta.data <- pbmc@meta.data %>% rename(
  cluster = predicted.celltype.l1,
  subcluster = predicted.celltype.l2
)

# Convert the Seurat object to an SCE object
pbmc.sce <- as.SingleCellExperiment(pbmc, assay = "RNA")
pbmc.sce
```

## Cluster-free DGE

First, we will estaimate neighborhood size to determine the optimal k to assign.

```{r}
stat_k = estimate_neighbourhood_sizes(pbmc.sce, k_grid = seq(10,40,5) , 
                                      order = 2, prop = 0.1 , filtering = TRUE,
                                      reducedDim_name = "HARMONY" , plot_stat = TRUE)

knitr::kable(stat_k , caption = "Neighbourhood size distribution ~ k")
```

Based on the above, I will use k = 30 for neighborhood size.

```{r}
gc()
set.seed(32)
milo_pbmc <- assign_neighbourhoods(pbmc.sce, k=30, order = 2,
                                   filtering = TRUE, reducedDim_name = "HARMONY")

# saveRDS(milo_pbmc, "Processing_RDS_files/milo_DE/2024_miloDE_pbmc_harmony_k30.rds")

gc()
milo_pbmc_35 <- assign_neighbourhoods(pbmc.sce, k=35, order = 2,
                                   filtering = TRUE, reducedDim_name = "HARMONY")

# saveRDS(milo_pbmc, "Processing_RDS_files/milo_DE/2024_miloDE_pbmc_harmony_k35.rds")

rm(list = setdiff(ls(), "milo_pbmc"))
gc()
```

Next, I will evaluate DGE in prednisone as my positive control.

```{r}
stat_auc = suppressWarnings(calc_AUC_per_neighbourhood(milo_pbmc , sample_id = "Sample_ID" , condition_id = "prednisone", min_n_cells_per_sample = 1, BPPARAM = SnowParam(16)))
saveRDS(stat_auc, "Processing_RDS_files/milo_DE/2024_stat_auc_prednisone_k30.rds")

stat_auc_0.5 <- filter(stat_auc, auc > 0.5)

gc()
de_stat_prednisone = de_test_neighbourhoods(milo_pbmc , sample_id = "Sample_ID", 
                                       design = ~prednisone, covariates = c("prednisone", "age", "sex"),
                                       subset_nhoods = stat_auc_0.5$Nhood, BPPARAM = SnowParam(16))

gc()
```


Save the above and run new code:

```{r}
gc()
saveRDS(de_stat_prednisone, "Processing_RDS_files/milo_DE/2024_de_stat_prednisone_k30.rds")
rm(de_stat_prednisone)

rm(list = setdiff(ls(), "milo_pbmc"))
gc()


# For high-grade CAV
stat_auc = suppressWarnings(calc_AUC_per_neighbourhood(milo_pbmc , sample_id = "Sample_ID" , condition_id = "high_grade_cav", min_n_cells_per_sample = 1, BPPARAM = SnowParam(16)))
saveRDS(stat_auc, "Processing_RDS_files/milo_DE/2024_stat_auc_high_grade_k30.rds")

stat_auc_0.5 <- filter(stat_auc, auc > 0.5)

gc()
de_stat_high = de_test_neighbourhoods(milo_pbmc , sample_id = "Sample_ID", 
                                 design = ~high_grade_cav, covariates = c("high_grade_cav", "age", "sex", "prednisone"),
                                 subset_nhoods = stat_auc_0.5$Nhood, BPPARAM = SnowParam(16))

gc()
saveRDS(de_stat_high, "Processing_RDS_files/milo_DE/2024_de_stat_high_grade_k30.rds")
```

Regular group:
```{r}
rm(list = setdiff(ls(), "milo_pbmc"))
gc()

stat_auc = suppressWarnings(calc_AUC_per_neighbourhood(milo_pbmc , sample_id = "Sample_ID" , condition_id = "group", min_n_cells_per_sample = 1, BPPARAM = SnowParam(16)))
saveRDS(stat_auc, "Processing_RDS_files/milo_DE/2024_stat_auc_group_k30.rds")

stat_auc_0.5 <- filter(stat_auc, auc > 0.5)

gc()
de_stat_group = de_test_neighbourhoods(milo_pbmc , sample_id = "Sample_ID", 
                                      design = ~group, covariates = c("group", "age", "sex", "prednisone"),
                                      subset_nhoods = stat_auc_0.5$Nhood, BPPARAM = SnowParam(16))

gc()
saveRDS(de_stat_group, "Processing_RDS_files/milo_DE/2024_de_stat_group_k30.rds")

```
