---
title: "Wrangling DE results"
author: "Kaushik Amancherla"
date: "2024-04-22"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(Seurat)
library(miloDE)
library(miloR)
library(SingleCellExperiment)
library(S4Vectors)
library(BiocParallel)
library(ggpubr)
library(gprofiler2)
library(viridis)
library(RColorBrewer)
library(clusterProfiler)
library(org.Hs.eg.db)
library(DOSE)

# Set working directory
setwd("C:/Users/amanchk/Downloads/PBMC_CAV_2.2024")
```

## Load RDS objects from the DE analysis

Here, I will load the DE objects I created using cluster-free DE analysis (miloDE) previously.

```{r}
# Prednisone vs non-prednisone
de_stat_pred <- readRDS("Processing_RDS_files/milo_DE/2024_de_stat_prednisone_k30.rds")

# High-grade CAV vs non-high-grade CAV
de_stat_high_grade <- readRDS("Processing_RDS_files/milo_DE/2024_de_stat_high_grade_k30.rds")
# write_csv(de_stat_high_grade, "Figures/DE_genes_high_grade_CAV.csv")

# Group (CAV vs non-CAV)
de_stat_group <- readRDS("Processing_RDS_files/milo_DE/2024_de_stat_group_k30.rds")
# write_csv(de_stat_group, "Figures/DE_genes_CAV.csv")

# Clear memory
gc()
```

## Loading the milo.pbmc RDS object (after assinging neighborhoods)

This will allow me to link the nhoods to celltypes:

```{r}
# Load object
milo.pbmc <- readRDS("Processing_RDS_files/milo_DE/2024_miloDE_pbmc_harmony_k30.rds")

# Annotate neighborhoods
nhoods_sce <- nhoods(milo.pbmc)

# Assign cell types for nhoods 
nhood_stat_ct <- data.frame(Nhood = 1:ncol(nhoods_sce) , Nhood_center = colnames(nhoods_sce))
nhood_stat_ct <- miloR::annotateNhoods(milo.pbmc , nhood_stat_ct , coldata_col = "subcluster")
```

## Visualization
Include only those genes significant both across genes and across neighborhoods.

High-grade CAV:
```{r}
# Joining subcluster info to nhoods
de_stat_high_grade <- inner_join(de_stat_high_grade, nhood_stat_ct, by = c("Nhood", "Nhood_center"))

# Volcano plot
ggplot(de_stat_high_grade, aes(x = logFC, y = -log10(pval), color = (pval_corrected_across_genes < 0.05 & pval_corrected_across_nhoods < 0.05))) +
  geom_point() +
  ggrepel::geom_text_repel(data = head((de_stat_high_grade %>% arrange(pval_corrected_across_genes)), 20), aes(label = gene)) +
  cowplot::theme_cowplot() +
  scale_color_manual(name = "FDR < 0.05", 
                     values = c("TRUE" = "red", "FALSE" = "black"),
                     labels = c("Not Significant", "Significant"))

# Save figure
# ggsave("Figures/volcano_plot_high_grade_cav_FDR.png", dpi = 1200, bg = "white")

# How many unique subclusters in this DE analysis?
length(unique(de_stat_high_grade$subcluster))

# Create custom colors for each subcluster
custom_colors <- c(
  "#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00",
  "#FFD700", "#A65628", "#F781BF", "#999999", "#66C2A5",
  "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"
)

# Cell-specific volcano plot
ggplot(de_stat_high_grade, aes(x = logFC, y = -log10(pval), color = subcluster)) +
  geom_point() +
  scale_color_manual(values = custom_colors) +
  ggrepel::geom_text_repel(data = head((de_stat_high_grade %>% arrange(pval_corrected_across_genes)), 20), aes(label = gene)) +
  cowplot::theme_cowplot()

# Save figure
# ggsave("Figures/volcano_high_grade_cell_specific.png", dpi = 1200, bg = "white")
```

CAV:
```{r}
# Joining subcluster info to nhoods
de_stat_group <- inner_join(de_stat_group, nhood_stat_ct, by = c("Nhood", "Nhood_center"))

# Volcano plot
ggplot(de_stat_group, aes(x = logFC, y = -log10(pval), color = (pval_corrected_across_genes < 0.05 & pval_corrected_across_nhoods < 0.05))) +
  geom_point() +
  ggrepel::geom_text_repel(data = head((de_stat_group %>% arrange(pval_corrected_across_genes)), 20), aes(label = gene)) +
  cowplot::theme_cowplot()  +
  scale_color_manual(name = "FDR < 0.05", 
                     values = c("TRUE" = "red", "FALSE" = "black"),
                     labels = c("Not significant", "Significant"))

# Save figure
# ggsave("Figures/volcano_plot_all_cav_FDR.png", dpi = 1200, bg = "white")

# How many unique subclusters in this DE analysis?
length(unique(de_stat_group$subcluster))

# Create custom colors
custom_colors_cav <- c(
  "#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00",
  "#FFD700", "#A65628", "#F781BF", "#999999", "#66C2A5",
  "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F",
  "#E5C494"
)

# Cell-specific volcano plot
ggplot(de_stat_group, aes(x = logFC, y = -log10(pval), color = subcluster)) +
  geom_point() +
  scale_color_manual(values = custom_colors_cav) +
  ggrepel::geom_text_repel(data = head((de_stat_group %>% arrange(pval_corrected_across_genes)), 20), aes(label = gene)) +
  cowplot::theme_cowplot()

# Save figure
# ggsave("Figures/volcano_all_cav_cell_specific.png", dpi = 1200, bg = "white")
```

Prednisone:
```{r}
# Joining subcluster info to nhoods
de_stat_pred <- inner_join(de_stat_pred, nhood_stat_ct, by = c("Nhood", "Nhood_center"))

# Volcano plot
ggplot(de_stat_pred, aes(x = logFC, y = -log10(pval), color = (pval_corrected_across_genes < 0.05 & pval_corrected_across_nhoods < 0.05))) +
  geom_point() +
  ggrepel::geom_text_repel(data = head((de_stat_pred %>% arrange(pval_corrected_across_genes)), 20), aes(label = gene)) +
  theme_bw()  +
  scale_color_manual(name = "FDR < 0.05", 
                     values = c("TRUE" = "red", "FALSE" = "black"),
                     labels = c("Not significant", "Significant"))

# Save figure
# ggsave("Figures/volcano_plot_prednisone_FDR.png", dpi = 1200, bg = "white")

# How many unique subclusters?
length(unique(de_stat_pred$subcluster))

# Create custom colors
custom_colors_pred <- c(
  "#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00",
  "#FFD700", "#A65628", "#F781BF", "#999999", "#66C2A5",
  "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"
)

# Cell-specific volcano plot
ggplot(de_stat_pred, aes(x = logFC, y = -log10(pval), color = subcluster)) +
  geom_point() +
  scale_color_manual(values = custom_colors_pred) +
  ggrepel::geom_text_repel(data = head((de_stat_pred %>% arrange(pval_corrected_across_genes)), 20), aes(label = gene)) +
  cowplot::theme_cowplot()

# Save figure
# ggsave("Figures/volcano_plot_prednisone_cell_specific.png", dpi = 1200, bg = "white")
```


## Testing modules

Next, we want to evaluate whether these significant genes fall into specific modules that are enriched for expected biological pathways in CAV. We will perform WGCNA for pval < 0.1 (to be exploratory). Instead of gene counts we will use corrected logFC (logFC set to 0 in the neighborhoods in which it is not DE).
```{r}
de_stat <- de_stat_high_grade
de_stat <- as.data.frame(de_stat)

get_wgcna_modules = function(de_stat, subset_hoods = NULL , 
                             n_hoods_sig.thresh = 2 ,
                             npcs = 5 ,
                             pval.thresh = 0.1 ){
  require(scWGCNA)
  require(Seurat)
  require(dplyr)
  require(reshape2)
  
  set.seed(32)
  # subset hoods
  if (!is.null(subset_hoods)){
    de_stat = de_stat[de_stat$Nhood %in% subset_hoods , ]
  }
  
  # focus on genes that DE in at least 2 nhoods
  de_stat_per_gene = de_stat %>% dplyr::group_by(gene) %>% dplyr::summarise(n_hoods_sig = sum(pval_corrected_across_nhoods < pval.thresh , na.rm = TRUE))
  genes_sig = de_stat_per_gene$gene[de_stat_per_gene$n_hoods_sig >= n_hoods_sig.thresh]
  
  de_stat = de_stat[de_stat$gene %in% genes_sig, ]
  de_stat = de_stat[order(de_stat$Nhood) , ]
  
  # discard neighbourhoods in which testing was not performed
  de_stat = de_stat[de_stat$test_performed , ]
  
  # for this analysis, set logFC to 0 and pvals to 1 if they are NaN
  de_stat$logFC[is.na(de_stat$logFC)] = 0
  de_stat$pval[is.na(de_stat$pval)] = 1
  de_stat$pval_corrected_across_genes[is.na(de_stat$pval_corrected_across_genes)] = 1
  de_stat$pval_corrected_across_nhoods[is.na(de_stat$pval_corrected_across_nhoods)] = 1
  
  # set logFC to 0 if pval_corrected_across_nhoods > pval.thresh
  de_stat$logFC[de_stat$pval_corrected_across_nhoods >= pval.thresh] = 0
  
  # move the object to Seurat
  de_stat = reshape2::dcast(data = de_stat, formula = gene~Nhood, value.var = "logFC")
  rownames(de_stat) = de_stat$gene
  de_stat = de_stat[,2:ncol(de_stat)]
  
  obj.seurat <- CreateSeuratObject(counts = de_stat)
  DefaultAssay(obj.seurat) <- "RNA"
  obj.seurat = FindVariableFeatures(obj.seurat)
  # scale
  obj.seurat[["RNA"]]@scale.data = as.matrix(obj.seurat[["RNA"]]@data)
  obj.seurat = RunPCA(obj.seurat , npcs = npcs)
  
  # run scwgcna
  clusters_scwgcna = run.scWGCNA(p.cells = obj.seurat, 
                                 s.cells = obj.seurat, 
                                 is.pseudocell = F, 
                                 features = rownames(obj.seurat),
                                 less = TRUE , merging = TRUE)
  # compile stat
  clusters = lapply(1:length(clusters_scwgcna$module.genes) , function(i){
    out = data.frame(cluster = i , gene = clusters_scwgcna$module.genes[[i]] , n_genes = length(clusters_scwgcna$module.genes[[i]]))
    return(out)
  })
  clusters = do.call(rbind , clusters)
  # add colors
  genes_w_colors = clusters_scwgcna$dynamicCols
  genes_w_colors = data.frame(gene = names(genes_w_colors) , cluster_color = genes_w_colors)
  clusters = merge(clusters , genes_w_colors)
  
  return(clusters)
}


# For simplicity we will focus on genes that are DE in at least 4 neighborhoods
modules_wgcna = suppressMessages(get_wgcna_modules(de_stat , n_hoods_sig.thresh = 4))

# Save csv file
# write_csv(modules_wgcna, "Figures/high_grade_modules_wgcna.csv")
```

## Pathway enrichment

First, I will do pseudobulk enrichment using all genes that were significantly DE in high-grade CAV vs all. Then, I will break it down by module. The entire list of genes tested (~17,000) will be used as background.

```{r}
# High-grade CAV - PSEUDOBULK
gene_high_grade <- de_stat_high_grade %>% filter(pval_corrected_across_genes < 0.05) %>% pull(gene)
gene_high_grade <- unique(gene_high_grade)

# Set background universe
background_high_grade <- de_stat_high_grade %>% pull(gene) %>% unique()

ego_high_grade <- enrichGO(
  gene = gene_high_grade,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)

# Visualize
dotplot(ego_high_grade, showCategory=20)

# Save figure
# ggsave("Figures/Enrichment_pseudobulk_high_grade_cav.png", dpi = 1200, bg = "white")

# Modules
module_1 <- modules_wgcna %>% filter(cluster == 1) %>% pull(gene)
ego_mod_1 <- enrichGO(
  gene = module_1,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)

module_2 <- modules_wgcna %>% filter(cluster == 2) %>% pull(gene)
ego_mod_2 <- enrichGO(
  gene = module_2,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)

module_3 <- modules_wgcna %>% filter(cluster == 3) %>% pull(gene)
ego_mod_3 <- enrichGO(
  gene = module_3,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)

module_4 <- modules_wgcna %>% filter(cluster == 4) %>% pull(gene)
ego_mod_4 <- enrichGO(
  gene = module_4,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(ego_mod_4)
dotplot(ego_mod_4, showCategory=20)

# Save figure
# ggsave("Figures/Enrichment_Module_4_high_grade.png", dpi = 1200, bg = "white")

module_5 <- modules_wgcna %>% filter(cluster == 5) %>% pull(gene)
ego_mod_5 <- enrichGO(
  gene = module_5,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(ego_mod_5)
dotplot(ego_mod_5, showCategory=20)

# Save figure
ggsave("Figures/Enrichment_Module_5_high_grade.png", dpi = 1200, bg = "white")

module_6 <- modules_wgcna %>% filter(cluster == 6) %>% pull(gene)
ego_mod_6 <- enrichGO(
  gene = module_6,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(ego_mod_6)

module_7 <- modules_wgcna %>% filter(cluster == 7) %>% pull(gene)
ego_mod_7 <- enrichGO(
  gene = module_7,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(ego_mod_7)
dotplot(ego_mod_7, showCategory=30)

# Save figure
ggsave("Figures/Enrichment_Module_7_high_grade.png", dpi = 1200, bg = "white", height = 15)

module_8 <- modules_wgcna %>% filter(cluster == 8) %>% pull(gene)
ego_mod_8 <- enrichGO(
  gene = module_8,
  universe = background_high_grade,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(ego_mod_8)
dotplot(ego_mod_8, showCategory=30)

# Save figure
# ggsave("Figures/Enrichment_Module_8_high_grade.png", dpi = 1200, bg = "white")
```
## Secondary analyses

I will now repeat what I've done above to the prednisone group and the CAV vs non-CAV group. These will be supplemental figures.

PREDNISONE:
```{r}
de_stat <- de_stat_pred
de_stat <- as.data.frame(de_stat)

get_wgcna_modules = function(de_stat, subset_hoods = NULL , 
                             n_hoods_sig.thresh = 2 ,
                             npcs = 5 ,
                             pval.thresh = 0.1 ){
  require(scWGCNA)
  require(Seurat)
  require(dplyr)
  require(reshape2)
  
  set.seed(32)
  # subset hoods
  if (!is.null(subset_hoods)){
    de_stat = de_stat[de_stat$Nhood %in% subset_hoods , ]
  }
  
  # focus on genes that DE in at least 2 nhoods
  de_stat_per_gene = de_stat %>% dplyr::group_by(gene) %>% dplyr::summarise(n_hoods_sig = sum(pval_corrected_across_nhoods < pval.thresh , na.rm = TRUE))
  genes_sig = de_stat_per_gene$gene[de_stat_per_gene$n_hoods_sig >= n_hoods_sig.thresh]
  
  de_stat = de_stat[de_stat$gene %in% genes_sig, ]
  de_stat = de_stat[order(de_stat$Nhood) , ]
  
  # discard neighbourhoods in which testing was not performed
  de_stat = de_stat[de_stat$test_performed , ]
  
  # for this analysis, set logFC to 0 and pvals to 1 if they are NaN
  de_stat$logFC[is.na(de_stat$logFC)] = 0
  de_stat$pval[is.na(de_stat$pval)] = 1
  de_stat$pval_corrected_across_genes[is.na(de_stat$pval_corrected_across_genes)] = 1
  de_stat$pval_corrected_across_nhoods[is.na(de_stat$pval_corrected_across_nhoods)] = 1
  
  # set logFC to 0 if pval_corrected_across_nhoods > pval.thresh
  de_stat$logFC[de_stat$pval_corrected_across_nhoods >= pval.thresh] = 0
  
  # move the object to Seurat
  de_stat = reshape2::dcast(data = de_stat, formula = gene~Nhood, value.var = "logFC")
  rownames(de_stat) = de_stat$gene
  de_stat = de_stat[,2:ncol(de_stat)]
  
  obj.seurat <- CreateSeuratObject(counts = de_stat)
  DefaultAssay(obj.seurat) <- "RNA"
  obj.seurat = FindVariableFeatures(obj.seurat)
  # scale
  obj.seurat[["RNA"]]@scale.data = as.matrix(obj.seurat[["RNA"]]@data)
  obj.seurat = RunPCA(obj.seurat , npcs = npcs)
  
  # run scwgcna
  clusters_scwgcna = run.scWGCNA(p.cells = obj.seurat, 
                                 s.cells = obj.seurat, 
                                 is.pseudocell = F, 
                                 features = rownames(obj.seurat),
                                 less = TRUE , merging = TRUE)
  # compile stat
  clusters = lapply(1:length(clusters_scwgcna$module.genes) , function(i){
    out = data.frame(cluster = i , gene = clusters_scwgcna$module.genes[[i]] , n_genes = length(clusters_scwgcna$module.genes[[i]]))
    return(out)
  })
  clusters = do.call(rbind , clusters)
  # add colors
  genes_w_colors = clusters_scwgcna$dynamicCols
  genes_w_colors = data.frame(gene = names(genes_w_colors) , cluster_color = genes_w_colors)
  clusters = merge(clusters , genes_w_colors)
  
  return(clusters)
}


# For simplicity we will focus on genes that are DE in at least 2 neighborhoods
modules_wgcna = suppressMessages(get_wgcna_modules(de_stat , n_hoods_sig.thresh = 2))

# Save csv file
# write_csv(modules_wgcna, "Figures/pred_modules_wgcna.csv")

# Pathway enrichment
# Prednisone vs others - PSEUDOBULK
gene_pred <- de_stat_pred %>% filter(pval_corrected_across_genes < 0.05) %>% pull(gene)
gene_pred <- unique(gene_pred)

# Set background universe
background_pred <- de_stat_pred %>% pull(gene) %>% unique()

ego_pred <- enrichGO(
  gene = gene_pred,
  universe = background_pred,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)

# Visualize
dotplot(ego_pred, showCategory=30)

# Save figure
ggsave("Figures/Enrichment_pseudobulk_prednisone.png", dpi = 1200, bg = "white", height = 15)

# Modules
pred_1 <- modules_wgcna %>% filter(cluster == 1) %>% pull(gene)
pred_mod_1 <- enrichGO(
  gene = pred_1,
  universe = background_pred,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(pred_mod_1)

pred_2 <- modules_wgcna %>% filter(cluster == 2) %>% pull(gene)
pred_mod_2 <- enrichGO(
  gene = pred_2,
  universe = background_pred,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(pred_mod_2)
```

While the "pseudobulk" results showed enrichment for pathways that are typically associated with glucocorticoids, neither of the two modules showed biological pathway enrichment.

CAV:
```{r}
de_stat <- de_stat_group
de_stat <- as.data.frame(de_stat)

get_wgcna_modules = function(de_stat, subset_hoods = NULL , 
                             n_hoods_sig.thresh = 2 ,
                             npcs = 5 ,
                             pval.thresh = 0.1 ){
  require(scWGCNA)
  require(Seurat)
  require(dplyr)
  require(reshape2)
  
  set.seed(32)
  # subset hoods
  if (!is.null(subset_hoods)){
    de_stat = de_stat[de_stat$Nhood %in% subset_hoods , ]
  }
  
  # focus on genes that DE in at least 2 nhoods
  de_stat_per_gene = de_stat %>% dplyr::group_by(gene) %>% dplyr::summarise(n_hoods_sig = sum(pval_corrected_across_nhoods < pval.thresh , na.rm = TRUE))
  genes_sig = de_stat_per_gene$gene[de_stat_per_gene$n_hoods_sig >= n_hoods_sig.thresh]
  
  de_stat = de_stat[de_stat$gene %in% genes_sig, ]
  de_stat = de_stat[order(de_stat$Nhood) , ]
  
  # discard neighbourhoods in which testing was not performed
  de_stat = de_stat[de_stat$test_performed , ]
  
  # for this analysis, set logFC to 0 and pvals to 1 if they are NaN
  de_stat$logFC[is.na(de_stat$logFC)] = 0
  de_stat$pval[is.na(de_stat$pval)] = 1
  de_stat$pval_corrected_across_genes[is.na(de_stat$pval_corrected_across_genes)] = 1
  de_stat$pval_corrected_across_nhoods[is.na(de_stat$pval_corrected_across_nhoods)] = 1
  
  # set logFC to 0 if pval_corrected_across_nhoods > pval.thresh
  de_stat$logFC[de_stat$pval_corrected_across_nhoods >= pval.thresh] = 0
  
  # move the object to Seurat
  de_stat = reshape2::dcast(data = de_stat, formula = gene~Nhood, value.var = "logFC")
  rownames(de_stat) = de_stat$gene
  de_stat = de_stat[,2:ncol(de_stat)]
  
  obj.seurat <- CreateSeuratObject(counts = de_stat)
  DefaultAssay(obj.seurat) <- "RNA"
  obj.seurat = FindVariableFeatures(obj.seurat)
  # scale
  obj.seurat[["RNA"]]@scale.data = as.matrix(obj.seurat[["RNA"]]@data)
  obj.seurat = RunPCA(obj.seurat , npcs = npcs)
  
  # run scwgcna
  clusters_scwgcna = run.scWGCNA(p.cells = obj.seurat, 
                                 s.cells = obj.seurat, 
                                 is.pseudocell = F, 
                                 features = rownames(obj.seurat),
                                 less = TRUE , merging = TRUE)
  # compile stat
  clusters = lapply(1:length(clusters_scwgcna$module.genes) , function(i){
    out = data.frame(cluster = i , gene = clusters_scwgcna$module.genes[[i]] , n_genes = length(clusters_scwgcna$module.genes[[i]]))
    return(out)
  })
  clusters = do.call(rbind , clusters)
  # add colors
  genes_w_colors = clusters_scwgcna$dynamicCols
  genes_w_colors = data.frame(gene = names(genes_w_colors) , cluster_color = genes_w_colors)
  clusters = merge(clusters , genes_w_colors)
  
  return(clusters)
}


# For simplicity we will focus on genes that are DE in at least 2 neighborhoods
modules_wgcna = suppressMessages(get_wgcna_modules(de_stat , n_hoods_sig.thresh = 2))

# Save csv file
# write_csv(modules_wgcna, "Figures/CAV_modules_wgcna.csv")

# Pathway enrichment
# CAV vs non-CAV - PSEUDOBULK
gene_cav <- de_stat_group %>% filter(pval_corrected_across_genes < 0.05) %>% pull(gene)
gene_cav <- unique(gene_cav)

# Set background universe
background_cav <- de_stat_group %>% pull(gene) %>% unique()

ego_cav <- enrichGO(
  gene = gene_cav,
  universe = background_cav,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)

# Visualize
dotplot(ego_cav, showCategory=30)

# Save figure
# ggsave("Figures/Enrichment_pseudobulk_CAV.png", dpi = 1200, bg = "white", height = 12)

# Modules
cav_1 <- modules_wgcna %>% filter(cluster == 1) %>% pull(gene)
cav_mod_1 <- enrichGO(
  gene = cav_1,
  universe = background_cav,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(cav_mod_1)

dotplot(cav_mod_1, showCategory=30)

# Save figure
# ggsave("Figures/Enrichment_Module_1_CAV.png", dpi = 1200, bg = "white")

cav_2 <- modules_wgcna %>% filter(cluster == 2) %>% pull(gene)
cav_mod_2 <- enrichGO(
  gene = cav_2,
  universe = background_cav,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(cav_mod_2)

cav_3 <- modules_wgcna %>% filter(cluster == 3) %>% pull(gene)
cav_mod_3 <- enrichGO(
  gene = cav_3,
  universe = background_cav,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(cav_mod_3)

cav_4 <- modules_wgcna %>% filter(cluster == 4) %>% pull(gene)
cav_mod_4 <- enrichGO(
  gene = cav_4,
  universe = background_cav,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(cav_mod_4)

cav_5 <- modules_wgcna %>% filter(cluster == 5) %>% pull(gene)
cav_mod_5 <- enrichGO(
  gene = cav_5,
  universe = background_cav,
  OrgDb = org.Hs.eg.db,
  keyType = "SYMBOL",
  ont = "BP",
  pAdjustMethod = "BH",
  pvalueCutoff  = 0.01,
  qvalueCutoff  = 0.05
)
head(cav_mod_5)

dotplot(cav_mod_5, showCategory=30)

# Save figure
# ggsave("Figures/Enrichment_Module_5_CAV.png", dpi = 1200, bg = "white")
```